\documentclass[11pt, a4paper]{article}

% --- PACKAGES DE BASE ---
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tabularx}

% --- CONFIGURATION DES POLICES ---
\usepackage{fontspec}
\usepackage[english]{babel}

% Utilisation de Noto Sans pour tout le document
\babelfont{rm}{Noto Sans}

% --- GESTION DES LISTES ---
\setlist[itemize]{label=-}

% --- COULEURS ET MARGES ---
\definecolor{light-grey}{gray}{0.85}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{0.15}
\definecolor{primary-blue}{RGB}{0, 74, 147}

\usepackage[top=1.0cm, bottom=1.0cm, left=1.2cm, right=1.2cm]{geometry}
\usepackage[hidelinks]{hyperref} % Loaded last as per guidelines

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- FORMATAGE DES SECTIONS ---
\titleformat{\section}{
  \bfseries \vspace{-2pt} \raggedright \large \color{primary-blue}
}{}{0em}{}[\color{light-grey} {\titlerule[1.5pt]} \vspace{-2pt}]

% --- COMMANDES PERSONNALISÉES ---
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{\small #3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  DÉBUT DU CV  %%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------EN-TÊTE----------
\begin{center}
    \textbf{\Huge Ben Fatma Imed} \\ \vspace{6pt}
    \large \textbf{Software Engineer | Java \& Next.js Developer} \\ \vspace{8pt}
    \small 
    Monastir, Tunisia $|$ 
    +216 51 198 800 $|$ 
    \href{mailto:imad.benfatma98@gmail.com}{imad.benfatma98@gmail.com} $|$ 
    \href{https://linkedin.com/in/imed-ben-fatma}{linkedin.com/in/imed-ben-fatma} 
\end{center}

%-----------RÉSUMÉ-----------
\section{PROFESSIONAL SUMMARY}
  \vspace{4pt}
  \small{Results-driven Software Engineer specializing in Java/Spring Boot and Next.js. Experienced in designing scalable web applications and utilizing AI-assisted tools to optimize performance and accelerate delivery in collaborative, distributed teams.}

%-----------EXPÉRIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Apeiron AI}{Aug. 2025 -- Present}
      {Software Engineer}{Sousse, Tunisia}
      \resumeItemListStart
        \resumeItem{Designed and integrated semantic analysis systems utilizing Large Language Models (\textbf{LLMs}).}
        \resumeItem{Architected and developed complex software solutions focused on scaling data and smart mobility pipelines.}
        \resumeItem{Digitized and optimized business processes via custom Next.js and backend integrations.}
        \resumeItem{Analyzed system performances and optimized database structures, achieving a \textbf{20\%} API latency reduction.}
      \resumeItemListEnd

    \resumeSubheading
      {Apeiron Technologies}{Feb. 2025 -- May 2025}
      {Software Engineer Intern}{Sousse, Tunisia}
      \resumeItemListStart
        \resumeItem{Analyzed and designed secure, production-ready backend architectures utilizing \textbf{Spring Boot}.}
        \resumeItem{Implemented relational database structures and built highly performant RESTful APIs.}
        \resumeItem{Leveraged AI-assisted programming tools to streamline clean code generation and optimize development lifecycles.}
        \resumeItem{Authored comprehensive technical documentation and system architecture specifications.}
      \resumeItemListEnd

    \resumeSubheading
      {Com-and-Dev}{June 2024 -- July 2024}
      {Software Developer Intern}{Sousse, Tunisia}
      \resumeItemListStart
        \resumeItem{Designed and developed a multi-user, full-stack business management application.}
        \resumeItem{Engineered robust, decoupled APIs to support seamless frontend-backend data flows.}
        \resumeItem{Created highly responsive UI layouts using modern web framework standards.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Terraform Tunisia}{Feb. 2024 -- Apr. 2024}
      {Software Engineer Intern}{Sousse, Tunisia}
      \resumeItemListStart
        \resumeItem{Gathered user requirements and developed a centralized platform utilizing \textbf{Next.js} and \textbf{Spring Boot}.}
        \resumeItem{Modeled and optimized highly performant relational database schemas under \textbf{PostgreSQL}.}
        \resumeItem{Participated in collaborative technical reviews to ensure codebase scalability and clean code quality.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------FORMATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {EPI Digital School}{2022 -- 2025}
      {National Engineering Degree in Computer Science}{Sousse, Tunisia}
    \resumeSubheading
      {ISET Kairouan}{2019 -- 2022}
      {Bachelor’s Degree in Automation and Industrial Computing}{Kairouan, Tunisia}
  \resumeSubHeadingListEnd

 %-----------COMPÉTENCES-----------
\section{TECHNICAL SKILLS \& ENGINEERING}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Software Engineering} {: OOP, Design Patterns, Software Architecture, Clean Code, SOLID Principles} \\ \vspace{2pt}
     \textbf{Languages \& Frameworks} {: Java, Python, TypeScript, Spring Boot, Next.js, React, Angular, Linux} \\ \vspace{2pt}
     \textbf{Databases \& Infrastructure} {: PostgreSQL, MySQL, SQL Server, Docker, Jenkins, Git, UML Modeling, CI/CD} \\ \vspace{2pt}
     \textbf{Methodologies \& Tools} {: Agile, Scrum, Requirements Analysis, AI Development Assistants (GitHub Copilot, LLMs)}
    }}
 \end{itemize}

%-----------LANGUAGES-----------
\section{LANGUAGES}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Arabic}: Native \quad $|$ \quad \textbf{English}: Professional Proficiency \quad $|$ \quad \textbf{French}: Fluent
    }}
 \end{itemize}

\end{document}
